---
title: "BOOSTING ALGORITHM"
# fn <- "2015-05-30-spark-not-docker.Rmd"
# library(knitr) ; knit(fn)  # produces the md file
# pandoc(fn, format = "docx") # prodces the .docx file
# permalink: If you need your processed blog post URLs to be something other than the default /year/month/day/title.html then you can set this variable and it will be used as the final URL.
date: "2015 June"
tags:
- R
- model
categories:
- rstat, boosting
# published = false => Jekyll will not process the file. Else Rmd file appears as a blog with html file i.e. 2 posts.
published: false 
# output: ioslides_presentation  
output:
  #  html_document:
  # http://rmarkdown.rstudio.com/html_fragment_format.html
  # html_fragment - no title or author -  excl std hdr content . HTML within larger web sites (e.g. blogs).
  html_fragment: 
    toc: true
    # theme: united
    number_sections: true
    keep_md: false
  # rmarkdown::render(fn) # produces table of contents and united theme
  # render(fn, pdf_document()) # library(rmarkdown) ; # knit2html() 
fontsize: 12pt
layout: post
author: "ttmmghmm"
---

# http://freakonometrics.hypotheses.org/19874

```{r}
n=300
set.seed(1)
u=sort(runif(n)*2*pi)
y=sin(u)+rnorm(n)/4
df=data.frame(x=u,y=y)
plot(df)
```

# linear-by-part regression models.
At each iterations, there are 7 parameters to ‘estimate’, the slopes and the nodes. 
consider some constant shrinkage parameter.
```{r, echo=FALSE}
v <- .05 
library(splines)
fit <- lm(y ~ bs(x, degree = 1, df = 3), data = df)
yp <- predict(fit, newdata = df)
df$yr <- df$y - v * yp
YP <- v * yp
```

This is the implementation of the algorithm described above,
```{r}
for(t in 1:100){
  fit=lm(yr~bs(x,degree=1,df=3),data=df)
  yp=predict(fit,newdata=df)
  df$yr=df$yr - v*yp
  YP=cbind(YP,v*yp)
}
str(YP)
```

The red line is the initial guess we have, without boosting, using a simple call of the regression function. 
The blue one is the one obtained using boosting. 
The dotted line is the true model.
```{r}
nd=data.frame(x=seq(0,2*pi,by=.01))
viz=function(M){
if(M==1)  y=YP[,1]
if(M>1)   y=apply(YP[,1:M],1,sum)
  plot(df$x,df$y,ylab="",xlab="")
  lines(df$x,y,type="l",col="red",lwd=3)
  fit=lm(y~bs(x,degree=1,df=3),data=df)
  yp=predict(fit,newdata=nd)
  lines(nd$x,yp,type="l",col="blue",lwd=3)
  lines(nd$x,sin(nd$x),lty=2)}

viz(50)
```
