---
title: "sparkline"
author: "ttmmghmm"
date: "1/10/2015"
output: html_document
---

http://www.htmlwidgets.org/develop_intro.html

https://github.com/htmlwidgets/sparkline



```{r installSparkline, eval = FALSE}
library(devtools)
install_github('htmlwidgets/sparkline')
```
Usage

The API is pretty simple
```{r API}
x = rnorm(20)
library(sparkline)
sparkline(x)
sparkline(x, type = 'bar')
sparkline(x, type = 'box')
```
You can also use it in an R Markdown document.

<pre>
---
title: "jquery Sparkline HTML Widget"
author: "Ramnath Vaidyanathan"
date: "July 18, 2014"
output: html_document
---
</pre>

```{r}
library(htmlwidgets)
library(sparkline)
set.seed(1234)
x = rnorm(10)
y = rnorm(10)
```


Inline line graphs `r sparkline(x)`

Bar charts  `r sparkline(abs(x), type = 'bar')`  negative values: `r sparkline(x, type = 'bar')`

| Stock | Sparkline         | Boxplot  
|-------|-------------------|--------
| x     | `r sparkline(x)`  | `r sparkline(x, type ='box')`
| y     | `r sparkline(y)`  | `r sparkline(y, type ='box')`