---
yamlFileName: 2015-01-02-TODOs.Rmd # WARNING: update the filename?
# setwd("~/git/ttmmghmm.github.io/_posts") ; library(knitr)
# fn <- "2015-01-02-TODOs.Rmd" ; knit(fn)  # to get the .md file 
# library(knitrBootstrap)
# rmarkdown::render(fn, knitrBootstrap::bootstrap_document(), clean = FALSE) # no md?
# https://github.com/jimhester/knitrBootstrap#bootstrap-themes
# produce an identical result to Knit HTML in RStudio- no run-time dependency on RStudio
#   knit(fn) ; markdownToHTML("foo.md") ; browseURL("foo.html")
# pandoc(fn, format = "docx") # prodces the .docx file - Word doc.
# rmarkdown::render(fn) # produces table of contents (and html?)
# rmarkdown::render(fn, pdf_document()) # and knit2html() to get .html from .md
title: List of TODOs # date: "2014 December" # (NULL) Set the title for the html document
#
# like categories, tags can be specified as a YAML list or a space- separated string.
# http://en.wikipedia.org/wiki/YAML#Lists
type: posts
layout: post
tags:
- Rwww
- plotwwww
categories: rstatswww dddd
# [ abc, def]
### everything (?) is a post and every post page is a bootstrap_document (?)
# published = false => Jekyll will not process Rmd file when site is generated
# Else Rmd file appears in the blog folders _posts, with html file, 
# i.e. 2 posts and Rmd file is unformatted. # http://jekyllrb.com/docs/frontmatter/
published: TRUE # over ridden by the exclude: ["*.Rmd", "_posts/*.md", in config.yml (?)
# permalink: If you need your processed blog post URLs to be something other than the default /year/month/day/title.html then you can set this variable and it will be used as the final URL.
output:
  # https://github.com/jimhester/knitrBootstrap
  # http://cran.r-project.org/web/packages/knitrBootstrap/README.html
  # ::bootstrap_document custom rendering function for the Rmarkdown package.
  knitrBootstrap::bootstrap_document: #  to create bootstrap styled HTML reports - not .md
    # https://github.com/jimhester/knitrBootstrap#package-options
    # title: "where does this appear? # (NULL) Set the title for the html document
    # http://bootswatch.com/ optionally including a dynamic style switch.
    theme: Cyborg # monokai cyborg slate darkly superhero cerulean 
    theme.chooser: TRUE # (FALSE) - Add a bootstrap style chooser to the page.
    # highlight Set the default code style. (HighlightJS)
    # https://github.com/jimhester/knitrBootstrap#highlight-themes
    highlight: monokai # Sunburst # Zenburn # HighlightJs # google code 
    highlight.chooser: TRUE # (FALSE) - Add a code style chooser to the page.
    menu: TRUE # FALSE # Whether to include the bottom navbar.
    # keep_md: is unused arguments for knitrBootstrap
  # html_fragment - no title or author -  excl std hdr content. 
  # this is for HTML within larger web sites (e.g. blogs).
  # http://rmarkdown.rstudio.com/html_fragment_format.html
  # html_fragment: 
  #   # cyborg     # united zenburn http://jekyllbootstrap.com/
  #   # theme: zenburn 
  #   keep_md: true
  #   toc: true
  #   number_sections: true
  # html_document:
  #   fig_caption: yes
  #   keep_md: yes
  #   number_sections: yes
  #   self_contained: no
  #   toc: yes
  #pdf_document:
  #  toc: true
  #  highlight: zenburn
# output: ioslides_presentation
author: ttmmghmm
# fontsize: 18pt # does it exist?
---

# Displaying an index of posts
http://jekyllrb.com/docs/posts/ says you can embed html and yaml variables.

* So does http://jekyllrb.com/docs/templates/
    * http://jekyllrb.com/docs/templates/
* http://rmarkdown.rstudio.com/ doesnt say anything?
* {% for post in site.posts %}
    <li>
      <a href="{{ post.url }}">{{ post.title }}</a>
    </li>
  {% endfor %}
<!-- http://jekyllrb.com/docs/collections/
{{  }}

{{ site.pos ts }}
{{ con tent }}
{{ out put }}
-->


# What they dont tell you about Rmarkdown
## Lists
1. Unordered lists should be a doddle but there are gotchas.
    * The first element in a list _must_ be preceeded by a blank line before the first item.
        * Ending the preceeding line with two or more spaces does not seem to work.
            * Even though it is documented to.
        * Neither does ending the line with html like < b r >.
            * TODO: how to do a literal quote.
    * You need to put two tabs at the start of a sub item.
        + Else the subitem will not render as a subitem in your list.

# Chunk options
* Avoid spaces and periods . in chunk labels and directory names
* https://github.com/jimhester/knitrBootstrap#chunk-options
    bootstrap.thumbnail: TRUE # Thumbnail and lightbox images.
    bootstrap.thumbnail.size: 'col-md-6' # size in bootstrap columns. (see Bootstrap Grid

## can change the default global options
https://github.com/jimhester/knitrBootstrap#chunk-options
```{r, eval = TRUE}
# https://github.com/jimhester/knitrBootstrap#chunk-options
# colors() [grep(patt = "dark", x = colours())]
#     panel: FALSE #  Use panels rather than buttons to toggle blocks.
opts_chunk$set(fig.width = 5, fig.height = 5)
# bootstrap.panel (FALSE) - panels rather than buttons to toggle blocks.
opts_chunk$set(background = c('gray10'), panel = TRUE) 
# http://getbootstrap.com/css/#grid
# bootstrap.thumbnail - (TRUE) - Thumbnail and lightbox images.
opts_chunk$set(thumbnail = TRUE, thumbnail.size = 'col-md-12')
# .class ('row') - class to apply to the div containing the chunk.
opts_chunk$set(class = 'rowew')
# bootstrap.show.code - (TRUE) - Code from this chunk starts as shown.
# opts_chunk$set(code = FALSE, output = FALSE) 
# opts_chunk$set(echo = FALSE, cache = FALSE)
# opts_chunk$set(message = FALSE, warning = FALSE, error = FALSE) 

# NOT working?
# The package options can be changed using the object opts_knit; for example,
opts_knit$set(progress = TRUE, verbose = TRUE)
```


```{r child = '../_posts/boiler_plate_vignette_setup.Rmd'}
# child: (NULL; character) a character vector of filenames of child documents to be run and input into the main document http://yihui.name/knitr/options/
# http://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output
```

```{r child = '../_posts/boiler_plate_bibliography_start.Rmd'}
```

# FlickR
http://www.omegahat.org/Rflickr/


# Twitter
http://stackoverflow.com/questions/20024047/oauth-issues-with-twitter-package

# GuardianR
* http://cran.r-project.org/web/packages/GuardianR/GuardianR.pdf
```{r 'GuardianR'}
library(GuardianR)
results <- get_guardian("islamic+state",
  from.date="2014-09-16",
  to.date="2014-09-16",
  api.key="3xzg2fk53jcdgaj5tbwqqhcz")
```

# TODO: how to add a caption?
```{r TODO: how to add a caption?}
# knitrBootstrap Images are automatically centered, thumbnailed and lightboxed using magnific popup.
# Code blocks automatically highlighted using highlight.js, optionally including a dynamic style switch.
# Code/Output block and plot visibility can be toggled with a mouse click
#   Globally and Per language
plot(rnorm(10))
```
TODO: how to add a caption?



* http://cran.r-project.org/web/packages/GuardianR/GuardianR.pdf


# Bitcoin
http://beautifuldata.net/2015/01/querying-the-bitcoin-blockchain-with-r/


# APIs
## public
http://opendata.stackexchange.com/questions/1677/a-web-api-users-guide-for-free-and-open-data?newsletter=1&nlcode=386863%7c20e3
  
# Wikipedia
* Tags: text mining
* Packages: tm

## Anomolies in page views
use the wikipediatrend package for convenience access statistics directly downloaded into your R-session. 
* http://cran.r-project.org/web/packages/wikipediatrend/index.html

See also [https://github.com/petermeissner/wikipediatrend] for a quick introduction to package use.

### http://beautifuldata.net/2015/01/anomaly-detection-with-wikipedia-page-view-data/

```{r}
library(RJSONIO)
library(RCurl)
library(ggplot2)
# install.packages("devtools")
# devtools::install_github("twitter/AnomalyDetection")
library(AnomalyDetection)
```

```{r}
page <- "USA"
raw_data <- getURL(paste("http://stats.grok.se/json/en/latest90/", page, sep=""))
data <- fromJSON(raw_data)
views <- data.frame(timestamp=paste(names(data$daily_views), " 12:00:00", sep=""), stringsAsFactors=F)
views$count <- data$daily_views
views$timestamp <- as.POSIXlt(views$timestamp) # Transform to POSIX datetime
views <- views[order(views$timestamp),]
```

```{r}
ggplot(views, aes(timestamp, count)) + geom_line() + scale_x_datetime() + xlab("") + ylab("views")
```
feed a dataframe with a date-time and a value column into the AnomalyDetection function AnomalyDetectionTs(). But in this case, this doesn’t work because our data is much too coarse

our data is much too coarse. It doesn’t seem to work with data on days. So, we use the more generic function AnomalyDetectionVec() that just needs the values and some definition of a period. In this case, the period is 7 (= 7 days for one week):
```{r}
res = AnomalyDetectionVec(views$count, max_anoms=0.05, direction='both', plot=TRUE, period=7)
res$plot
```


If you want to do this with more time points though, use the wikipediatrend package for convenience access statistics directly downloaded into your R-session. 
http://cran.r-project.org/web/packages/wikipediatrend/index.html
See also [https://github.com/petermeissner/wikipediatrend] for a quick introduction to package use.

### wikipediatrend
```{r}
require(wikipediatrend)

system.time(df <- 
  wp_trend(
    page = "Peter_principle" # the name of the page
    , from = Sys.Date()-30 # starting date of the timespan to be considered
    , to = Sys.Date() #  end date of the timespan to be considered
    , lang = "en" # language of the page
    , friendly = FALSE # minimize workload on behalf of stats.grok.se
    , requestFrom = "anonymous" # identify yourself towards stats.grok.se
    , userAgent = FALSE # send information - plattform, R version, package used to make server requests
  ) 
)
```
It shows us which URLs it used to retrieve the information we were asking for.

The function's return is a data frame with two variables date and count:
```{r return is a data frame with two variables date and count}
str(df)
```

visualize the page view trend. 
Using wp_wday() we can furthermore discriminate weekdays (black) from weekends (red).
```{r}
peter_principle <- df
plot( peter_principle, 
      col=ifelse( wp_wday(peter_principle$date) > 5 , "red", "black") ,
      ylim=c(0, max(peter_principle$count)),
      main="Peter Principle's Wikipedia Attention",
      ylab="views per day", xlab="time")
lines(peter_principle)
```
most pressing on workdays -- or maybe people in general just tend to use their computers less on weekends.

### friendly
friendly option can be set to different values:
* FALSE, the default, deactivates wp_trend()'s friendly behavior altogether
* TRUE, activates wp_trend()'s friendly behavior and retreieved access statistics are stored on disk in CSV format via write.csv()
* 1 is the same as TRUE
* 2, is the same as TRUE but storage takes place via write.csv2()
Let's try it out by making two subsequent requests to get access statistics for for information on ISIS.

```{r}
csv <- "wp__Islamic_State_of_Iraq_and_the_Levant__en.csv"
if (file.exists(csv)) file.remove(csv)
isis <- wp_trend("Islamic_State_of_Iraq_and_the_Levant", from="2013-01-01", friendly=T)
```


http://beautifuldata.net/2015/01/anomaly-detection-with-wikipedia-page-view-data/


## Graph and web crawling
* http://semanticweb.cs.vu.nl/R/wikipedia_graph/wikipedia_graph.html
* Tags: [text mining, graphs, wikipedia, crawl, Simple Wikipedia, Wikipedia,
  analytical metrics]
  * ???Basic English 850 basic English words chosen by Charles Kay Ogden.???
* TODO: dynamic graph, shiny

## WikiPediR package
* http://www.rexamine.com/2014/06/text-mining-in-r-automatic-categorization-of-wikipedia-articles/
  *  hierarchical categorization of Wikipedia articles
* more information about text mining in R: 
    * http://onepager.togaware.com/TextMiningO.pdf
    * http://cran.r-project.org/web/views/NaturalLanguageProcessing.html
    * http://www.r-bloggers.com/text-mining/
    * http://cran.r-project.org/doc/contrib/Zhao_R_and_data_mining.pdf
    * http://www.jstatsoft.org/v25/i05/paper
    * http://www.r-bloggers.com/visualising-wikipedia-search-statistics-with-r/
        * search traffic for any article - search statistics for ???Financial crisis???. 
            * The wikiStat() function returns dataframe with the necessary data.
    * http://cran.r-project.org/web/packages/tm.plugin.webmining/vignettes/ShortIntro.pdf

# Databases
* MongoDB 
    * http://demo.ocpu.io/jsonlite/man/stream_in/html
    * http://cran.r-project.org/web/packages/jSonarR/index.html
* http://www.exmachinatech.net/projects/factualR/

# Shiny
* https://dl.dropboxusercontent.com/u/5728437/r-in-fashion.html

# streaming
* streamR: Access to Twitter Streaming API via R
    * * http://cran.r-project.org/web/packages/streamR/index.html 

# scraping
* http://cran.r-project.org/web/packages/RSelenium/index.html

# cloud 
* https://github.com/sckott/analogsea

# packages
* http://www.omegahat.org/Rflickr/
* gmailr gmailr: Access the Gmail RESTful API
    * http://cran.r-project.org/web/packages/gmailr/index.html
* http://cran.r-project.org/web/packages/tumblR/index.html
* http://cran.r-project.org/web/packages/twitteR/index.html
    * http://freakonometrics.hypotheses.org/18605
* http://cran.r-project.org/web/packages/wikipediatrend/index.html
* Hacking the Google Trends API
    * http://techslides.com/hacking-the-google-trends-api
* http://things-about-r.tumblr.com/post/106806522699/change-point-detection-in-time-series-with-r-and


# presentations
* http://gastonsanchez.com/work/webdata/
    * http://gastonsanchez.com/work/webdata/getting_web_data_r8_web_apis.pdf
* http://www.theresearchkitchen.com/archives/1017

```{r docs not evaluated, eval = FALSE}
opts_chunk$set(eval = FALSE)
library(magrittr)
docs[[1]]
# Replace all ?????? elements with a space. 
# We do it because there are not a part of text document but in general a html code.
# use the non-greedy .*? match - match up until the first following instance of '>'. Without this, if you use just .*, you'll capture everything up to the last '[END DATA]'>'.
docs2 <- tm_map(docs, function(x) stri_replace_all_regex(x, "<.+?>", " "))
docs3 <- tm_map(docs2, function(x) stri_replace_all_fixed(x, "\t", " "))
docs2[[1]]

docs4 <- tm_map(docs3, PlainTextDocument)
docs5 <- tm_map(docs4, stripWhitespace)
docs6 <- tm_map(docs5, removeWords, stopwords("english"))
docs7 <- tm_map(docs6, removePunctuation)
docs8 <- tm_map(docs7, tolower)

docs8[[1]]

docs %>% 
  tm_map(FUN = function(x) stri_replace_all_regex(x, "<.+?>", " ")) ->  
docs2 
```



```{r child = '../_posts/boiler_plate_reproducibility.Rmd'}
```

<!-- 
# boiler_plate_bibliography_end has to come last else references in boiler_plate_reproducibility are lost!
-->
```{r child = '../_posts/boiler_plate_bibliography_end.Rmd'}
```

