---
yamlFileName: 2015-01-27-quandl.Rmd # WARNING: update the filename?
# print(rmarkdown::metadata$yamlFileName) # permalink
# library(knitr)
# setwd("~/git/ttmmghmm.github.io/_posts") ; fn <- "2015-01-10-quandl.Rmd" ; knit(fn)  # to get the .md file 
#
# library(knitrBootstrap)
# rmarkdown::render(fn, knitrBootstrap::bootstrap_document(), clean = FALSE) # no md?
# produce an identical result to Knit HTML in RStudio- no run-time dependency on RStudio
# https://github.com/jimhester/knitrBootstrap#bootstrap-themes
#   knit(fn) ; markdownToHTML("foo.md") ; browseURL("foo.html")
# pandoc(fn, format = "docx") # prodces the .docx file - Word doc.
# rmarkdown::render(fn) # produces table of contents (and html?)
# rmarkdown::render(fn, pdf_document()) # and knit2html() to get .html from .md
title: "stochvolR example"
#
# like categories, tags can be specified as a YAML list or a space- separated string.
# http://en.wikipedia.org/wiki/YAML#Lists
type: posts
layout: post
tags:
- R
- D3 network
categories: rstats networkD3
output:
  # https://github.com/jimhester/knitrBootstrap
  # http://cran.r-project.org/web/packages/knitrBootstrap/README.html
  # ::bootstrap_document custom rendering function for the Rmarkdown package.
  knitrBootstrap::bootstrap_document: #  to create bootstrap styled HTML reports - not .md
    # https://github.com/jimhester/knitrBootstrap#package-options
    title: where does this appear? # (NULL) Set the title for the html document
    # http://bootswatch.com/ optionally including a dynamic style switch.
    theme: Cyborg # cerulean # Cyborg # monokai cyborg slate darkly superhero cerulean 
    theme.chooser: TRUE # (FALSE) - Add a bootstrap style chooser to the page.
    # highlight Set the default code style. (HighlightJS)
    # https://github.com/jimhester/knitrBootstrap#highlight-themes
    highlight: monokai # Zenburn # monokai # Sunburst # Zenburn # HighlightJs # google code 
    highlight.chooser: TRUE # (FALSE) - Add a code style chooser to the page.
    menu: TRUE # FALSE # Whether to include the bottom navbar.
author: ttmmghmm
---

```{r child = c('../_posts/boiler_plate_vignette_setup.Rmd', '../_posts/boiler_plate_bibliography_start.Rmd') }
# child: (NULL; character) a character vector of filenames of child documents to be run and input into the main document http://yihui.name/knitr/options/
# http://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output
```



# Quandl

Perform a once off task of storing access token for Quandl.
See <https://github.com/hadley/secure>.
```{r, eval=FALSE, bootstrap.show.code=FALSE, bootstrap.show.message=FALSE, bootstrap.show.output=FALSE}
library(secure)
# Create a vault directory in your working directory.
stopifnot(file.exists("vault"))
# add your name and public key to vault/users.json
# secure::add_user("ttmmghmm", local_key())
# add other people from their github_key()s).
# store data securly
secure::encrypt(
  "quandl", 
  key = "Quandl.auth", # https://www.quandl.com/account
  secret = "")
# This creates secure/google.rds.enc, an encrypted rds file.
```

# Set your Quandl access token
Retrieve encrypted data via the `secure` package.
See <https://github.com/hadley/secure>.
```{r}
library(magrittr)
library(Quandl) # https://www.quandl.com/account
library(secure)
# This decrypts the encrypted file using your private key.
myQuandl <- secure::decrypt("quandl") # Quandl.auth("yourauthenticationtoken")
myQuandl$secret %>% (myQuandl$key %>% get) # Quandl.auth("myQuandl$secret")
# Save the token object for future sessions
#save(token, file="./token_file")
```

# Basic futures data
Just pick a dataset and enter its Quandl code, like this:
```{r}
(c("FRED/GDP.1", "NSE/OIL.4","WIKI/AAPL.3") %>% 
  Quandl(., type="xts")   ->
  mydata)                 %>%
  str
```
Data in 4 formats: 
* data frame ("raw") (default)
* ts ("ts")
* zoo ("zoo")
* xts ("xts"). 

Get multiple datasets in one call by passing an array of Quandl codes, like this:
`mydata = Quandl(c("NSE/OIL.4","WIKI/AAPL.1"))`.
This grabs the 4th column of dataset NSE/OIL and the 1st column of dataset WIKI/AAPL, and returns them in a single call.

# Search Quandl for datasets 
## Gold futures
```{r}
# str(Quandl.search(query = "crude oil", page = 2, source = "DOE", silent = TRUE))
(("gold" %>% 
  Quandl.search(query = ., source = "CME", silent = TRUE)) ->
  gold) %>%
  str
```
The only mandatory parameter is "query". 
* "page" specifies which page of search results you wish to see (default=1). 
* "source" specifies that you want to search within a particular data source (default=all data sources). 
* "silent" specifies whether or not you want to see the first 3 results on the console.

Extract the code names.
```{r}
gold %>%
  sapply(., "[[", "code") ->
  goldCode
```

Order by date of expiry.
```{r}
(goldCode %>%
  gsub(patt = "(.+)([[:upper:]])([[:digit:]]{4})$", repl = "\\3-\\2", x = .) ->
  yearMth) %>% 
  str
(yearMth %>%
  order %>%
  extract(goldCode, .) ->
  goldCodeOrd) %>%
  str
```
Now grab the individual expiry-ordered futures
```{r}
system.time(
  goldCodeOrd %>%
    lapply(., FUN = Quandl, type="xts") ->
    futsGold
)
names(futsGold) <- goldCodeOrd
futsGold %>% length
futsGold %>% extract(1) %>% str
futsGold %>% extract2(1) %>% tail
```

Look at open interest
```{r}
futsGold
```


```{r, eval=FALSE}
my_db <- src_sqlite("my_db.sqlite3", create = T)
copy_to(my_db, futsGold, temporary = FALSE, 
  indexes = list(c("year", "month", "day"), "carrier", "tailnum")
)
tbl(my_db, sql("SELECT * FROM flights"))
```

```{r}
(goldCode %>% 
  Quandl(., type="xts")   ->
  mydata)                 %>%
  str
```




```{r child = c('../_posts/boiler_plate_reproducibility.Rmd', '../_posts/boiler_plate_bibliography_end.Rmd') }
```
