---
yamlFileName: 2015-01-02-TODOs.Rmd # WARNING: update the filename?
# fn <- "2015-01-02-TODOs.Rmd" ; knit(fn)  # to get the .md file 
# library(knitrBootstrap)
# rmarkdown::render(fn, knitrBootstrap::bootstrap_document(), clean = FALSE) # no md?
# https://github.com/jimhester/knitrBootstrap#bootstrap-themes
# produce an identical result to Knit HTML in RStudio- no run-time dependency on RStudio
#   knit(fn) ; markdownToHTML("foo.md") ; browseURL("foo.html")
# pandoc(fn, format = "docx") # prodces the .docx file - Word doc.
# rmarkdown::render(fn) # produces table of contents (and html?)
# rmarkdown::render(fn, pdf_document()) # and knit2html() to get .html from .md
title: List of TODOs # date: "2014 December" # (NULL) Set the title for the html document
#
# like categories, tags can be specified as a YAML list or a space- separated string.
# http://en.wikipedia.org/wiki/YAML#Lists
type: posts
layout: post
tags:
- Rwww
- plotwwww
categories: rstatswww dddd
# [ abc, def]
### everything (?) is a post and every post page is a bootstrap_document (?)
# published = false => Jekyll will not process Rmd file when site is generated
# Else Rmd file appears in the blog folders _posts, with html file, 
# i.e. 2 posts and Rmd file is unformatted. # http://jekyllrb.com/docs/frontmatter/
published: TRUE # over ridden by the exclude: ["*.Rmd", "_posts/*.md", in config.yml (?)
# permalink: If you need your processed blog post URLs to be something other than the default /year/month/day/title.html then you can set this variable and it will be used as the final URL.
output:
  # https://github.com/jimhester/knitrBootstrap
  # http://cran.r-project.org/web/packages/knitrBootstrap/README.html
  # ::bootstrap_document custom rendering function for the Rmarkdown package.
  knitrBootstrap::bootstrap_document: #  to create bootstrap styled HTML reports - not .md
    # https://github.com/jimhester/knitrBootstrap#package-options
    # title: "where does this appear? # (NULL) Set the title for the html document
    # http://bootswatch.com/ optionally including a dynamic style switch.
    theme: Cyborg # monokai cyborg slate darkly superhero cerulean 
    theme.chooser: TRUE # (FALSE) - Add a bootstrap style chooser to the page.
    # highlight Set the default code style. (HighlightJS)
    # https://github.com/jimhester/knitrBootstrap#highlight-themes
    highlight: monokai # Sunburst # Zenburn # HighlightJs # google code 
    highlight.chooser: TRUE # (FALSE) - Add a code style chooser to the page.
    menu: TRUE # FALSE # Whether to include the bottom navbar.
    # keep_md: is unused arguments for knitrBootstrap
  # html_fragment - no title or author -  excl std hdr content. 
  # this is for HTML within larger web sites (e.g. blogs).
  # http://rmarkdown.rstudio.com/html_fragment_format.html
  # html_fragment: 
  #   # cyborg     # united zenburn http://jekyllbootstrap.com/
  #   # theme: zenburn 
  #   keep_md: true
  #   toc: true
  #   number_sections: true
  # html_document:
  #   fig_caption: yes
  #   keep_md: yes
  #   number_sections: yes
  #   self_contained: no
  #   toc: yes
  #pdf_document:
  #  toc: true
  #  highlight: zenburn
# output: ioslides_presentation
author: ttmmghmm
# fontsize: 18pt # does it exist?
---

# Displaying an index of posts
http://jekyllrb.com/docs/posts/ says you can embed html and yaml variables.

* So does http://jekyllrb.com/docs/templates/
    * http://jekyllrb.com/docs/templates/
* http://rmarkdown.rstudio.com/ doesnt say anything?
* {% for post in site.posts %}
    <li>
      <a href="{{ post.url }}">{{ post.title }}</a>
    </li>
  {% endfor %}
<!-- http://jekyllrb.com/docs/collections/
{{  }}

{{ site.pos ts }}
{{ con tent }}
{{ out put }}
-->


# What they dont tell you about Rmarkdown
## Lists
1. Unordered lists should be a doddle but there are gotchas.
    * The first element in a list _must_ be preceeded by a blank line before the first item.
        * Ending the preceeding line with two or more spaces does not seem to work.
            * Even though it is documented to.
        * Neither does ending the line with html like < b r >.
            * TODO: how to do a literal quote.
    * You need to put two tabs at the start of a sub item.
        + Else the subitem will not render as a subitem in your list.

# Chunk options
* Avoid spaces and periods . in chunk labels and directory names
* https://github.com/jimhester/knitrBootstrap#chunk-options
    bootstrap.thumbnail: TRUE # Thumbnail and lightbox images.
    bootstrap.thumbnail.size: 'col-md-6' # size in bootstrap columns. (see Bootstrap Grid

## can change the default global options
https://github.com/jimhester/knitrBootstrap#chunk-options
```{r, eval = TRUE}
library(knitr) # is this needed here?
# https://github.com/jimhester/knitrBootstrap#chunk-options
# colors() [grep(patt = "dark", x = colours())]
#     panel: FALSE #  Use panels rather than buttons to toggle blocks.
opts_chunk$set(fig.width = 5, fig.height = 5)
# bootstrap.panel (FALSE) - panels rather than buttons to toggle blocks.
opts_chunk$set(background = c('gray10'), panel = TRUE) 
# http://getbootstrap.com/css/#grid
# bootstrap.thumbnail - (TRUE) - Thumbnail and lightbox images.
opts_chunk$set(thumbnail = TRUE, thumbnail.size = 'col-md-12')
# .class ('row') - class to apply to the div containing the chunk.
opts_chunk$set(class = 'rowew')
# bootstrap.show.code - (TRUE) - Code from this chunk starts as shown.
# opts_chunk$set(code = FALSE, output = FALSE) 
# opts_chunk$set(echo = FALSE, cache = FALSE)
# opts_chunk$set(message = FALSE, warning = FALSE, error = FALSE) 

# NOT working?
# The package options can be changed using the object opts_knit; for example,
opts_knit$set(progress = TRUE, verbose = TRUE)
```


```{r child = '../_posts/boiler_plate_vignette_setup.Rmd'}
# child: (NULL; character) a character vector of filenames of child documents to be run and input into the main document http://yihui.name/knitr/options/
# http://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output
```

```{r child = '../_posts/boiler_plate_bibliography_start.Rmd'}
```



# Twitter
http://stackoverflow.com/questions/20024047/oauth-issues-with-twitter-package

# GuardianR
```{r 'GuardianR'}
library(GuardianR)
results <- get_guardian("islamic+state",
  from.date="2014-09-16",
  to.date="2014-09-16",
  api.key="3xzg2fk53jcdgaj5tbwqqhcz")
```

# TODO: how to add a caption?
```{r TODO: how to add a caption?}
# knitrBootstrap Images are automatically centered, thumbnailed and lightboxed using magnific popup.
# Code blocks automatically highlighted using highlight.js, optionally including a dynamic style switch.
# Code/Output block and plot visibility can be toggled with a mouse click
#   Globally and Per language
plot(rnorm(10))
```
TODO: how to add a caption?



* http://cran.r-project.org/web/packages/GuardianR/GuardianR.pdf


# Bitcoin
http://beautifuldata.net/2015/01/querying-the-bitcoin-blockchain-with-r/


# APIs
## public
http://opendata.stackexchange.com/questions/1677/a-web-api-users-guide-for-free-and-open-data?newsletter=1&nlcode=386863%7c20e3
  
# Wikipedia
* Tags: text mining
* Packages: tm

## Graph and web crawling
* http://semanticweb.cs.vu.nl/R/wikipedia_graph/wikipedia_graph.html
* Tags: [text mining, graphs, wikipedia, crawl, Simple Wikipedia, Wikipedia,
  analytical metrics]
  * ???Basic English 850 basic English words chosen by Charles Kay Ogden.???
* TODO: dynamic graph, shiny

## WikiPediR package
* http://www.rexamine.com/2014/06/text-mining-in-r-automatic-categorization-of-wikipedia-articles/
  *  hierarchical categorization of Wikipedia articles
* more information about text mining in R: 
    * http://onepager.togaware.com/TextMiningO.pdf
    * http://cran.r-project.org/web/views/NaturalLanguageProcessing.html
    * http://www.r-bloggers.com/text-mining/
    * http://www.jstatsoft.org/v25/i05/paper
    * http://www.r-bloggers.com/visualising-wikipedia-search-statistics-with-r/
        * search traffic for any article - search statistics for ???Financial crisis???. 
            * The wikiStat() function returns dataframe with the necessary data.
    * http://cran.r-project.org/web/packages/tm.plugin.webmining/vignettes/ShortIntro.pdf

```{r docs not evaluated, eval = FALSE}
opts_chunk$set(eval = FALSE)
library(magrittr)
docs[[1]]
# Replace all ?????? elements with a space. 
# We do it because there are not a part of text document but in general a html code.
# use the non-greedy .*? match - match up until the first following instance of '>'. Without this, if you use just .*, you'll capture everything up to the last '[END DATA]'>'.
docs2 <- tm_map(docs, function(x) stri_replace_all_regex(x, "<.+?>", " "))
docs3 <- tm_map(docs2, function(x) stri_replace_all_fixed(x, "\t", " "))
docs2[[1]]

docs4 <- tm_map(docs3, PlainTextDocument)
docs5 <- tm_map(docs4, stripWhitespace)
docs6 <- tm_map(docs5, removeWords, stopwords("english"))
docs7 <- tm_map(docs6, removePunctuation)
docs8 <- tm_map(docs7, tolower)

docs8[[1]]

docs %>% 
  tm_map(FUN = function(x) stri_replace_all_regex(x, "<.+?>", " ")) ->  
docs2 
```



```{r child = '../_posts/boiler_plate_reproducibility.Rmd'}
```

<!-- 
# boiler_plate_bibliography_end has to come last else references in boiler_plate_reproducibility are lost!
-->
```{r child = '../_posts/boiler_plate_bibliography_end.Rmd'}
```

