---
yamlFileName: 2015-01-02-TODOs.Rmd # WARNING: update the filename?
title: List of TODOs
author: ttmmghmm
layout: post
# library(knitr) ; fn <- "foo.Rmd" ; knit(fn)  # produces the md file
# pandoc(fn, format = "docx") # prodces the .docx file - Word doc.
# produce an identical result to Knit HTML in RStudio- no run-time dependency on RStudio
#   knit(fn) ; markdownToHTML("foo.md") ; browseURL("foo.html")
output:
  html_document:
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    self_contained: no
    toc: yes
tags:
- "Rs as"
- plota as asdf
categories: rstatsas dadf as
# published = false => Jekyll will not process Rmd file. 
# Else Rmd file appears in the blog folders _posts, with html file, 
# i.e. 2 posts and Rmd file is unformatted.
published: false 
---


# What they dont tell you about Rmarkdown
## Lists
* Unordered lists should be a doddle but there are gotchas.
* The first element in a list _must_ be preceeded by a blank line before the first item.
    * Ending the preceeding line with two or more spaces does not seem to work.
        * Even though it is documented to.
    * Neither does ending the line with html like < b r >.
        * TODO: how to do a literal quote.
* You need to put two tabs at the start of a sub item.
    + Else the subitem will not render as a subitem in your list.



```{r child = '../_posts/boiler_plate_vignette_setup.Rmd'}
# http://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output
```

```{r child = '../_posts/boiler_plate_bibliography_start.Rmd'}
```

# Twitter
http://stackoverflow.com/questions/20024047/oauth-issues-with-twitter-package

# GuardianR
```{r 'GuardianR'}
library(GuardianR)
results <- get_guardian("islamic+state",
  from.date="2014-09-16",
  to.date="2014-09-16",
  api.key="3xzg2fk53jcdgaj5tbwqqhcz")
```

```{r}
plot(rnorm(10))
```



* http://cran.r-project.org/web/packages/GuardianR/GuardianR.pdf


# Bitcoin
http://beautifuldata.net/2015/01/querying-the-bitcoin-blockchain-with-r/


# APIs
## public
http://opendata.stackexchange.com/questions/1677/a-web-api-users-guide-for-free-and-open-data?newsletter=1&nlcode=386863%7c20e3
  
# Wikipedia
* Tags: text mining
* Packages: tm

## Graph and web crawling
* http://semanticweb.cs.vu.nl/R/wikipedia_graph/wikipedia_graph.html
* Tags: [text mining, graphs, wikipedia, crawl, Simple Wikipedia, Wikipedia,
  analytical metrics]
  * “Basic English 850 basic English words chosen by Charles Kay Ogden.”
* TODO: dynamic graph, shiny

## WikiPediR package
* http://www.rexamine.com/2014/06/text-mining-in-r-automatic-categorization-of-wikipedia-articles/
  *  hierarchical categorization of Wikipedia articles
* more information about text mining in R: 
    * http://onepager.togaware.com/TextMiningO.pdf
    * http://cran.r-project.org/web/views/NaturalLanguageProcessing.html
    * http://www.r-bloggers.com/text-mining/
    * http://www.jstatsoft.org/v25/i05/paper
    * http://www.r-bloggers.com/visualising-wikipedia-search-statistics-with-r/
        * search traffic for any article - search statistics for “Financial crisis”. 
            * The wikiStat() function returns dataframe with the necessary data.
    * http://cran.r-project.org/web/packages/tm.plugin.webmining/vignettes/ShortIntro.pdf

```{r, eval = FALSE}
opts_chunk$set(eval = FALSE)
library(magrittr)
docs[[1]]
# Replace all “” elements with a space. 
# We do it because there are not a part of text document but in general a html code.
# use the non-greedy .*? match - match up until the first following instance of '>'. Without this, if you use just .*, you'll capture everything up to the last '[END DATA]'>'.
docs2 <- tm_map(docs, function(x) stri_replace_all_regex(x, "<.+?>", " "))
docs3 <- tm_map(docs2, function(x) stri_replace_all_fixed(x, "\t", " "))
docs2[[1]]

docs4 <- tm_map(docs3, PlainTextDocument)
docs5 <- tm_map(docs4, stripWhitespace)
docs6 <- tm_map(docs5, removeWords, stopwords("english"))
docs7 <- tm_map(docs6, removePunctuation)
docs8 <- tm_map(docs7, tolower)

docs8[[1]]

docs %>% 
  tm_map(FUN = function(x) stri_replace_all_regex(x, "<.+?>", " ")) ->  
docs2 
```





```{r child = '../_posts/boiler_plate_reproducibility.Rmd'}
```

```{r child = '../_posts/boiler_plate_bibliography_end.Rmd'}
# boiler_plate_bibliography_end has to come last else references in boiler_plate_reproducibility are lost!
```

