---
yamlFileName: 2015-01-11-minimal.Rmd # WARNING: update the filename?
# print(rmarkdown::metadata$yamlFileName) # permalink
# library(knitr)
# to get the .md file only 
# setwd("~/git/ttmmghmm.github.io/_posts") ; fn <- "2015-01-11-minimal.Rmd" ; knit(fn)  
#
# library(knitrBootstrap)
# # clean = FALSE => two md files? why
# rmarkdown::render(fn, knitrBootstrap::bootstrap_document(), clean = FALSE) 
# produce an identical result to Knit HTML in RStudio- no run-time dependency on RStudio
# https://github.com/jimhester/knitrBootstrap#bootstrap-themes
#   knit(fn) ; markdown::markdownToHTML("2015-01-11-minimal.md") ; browseURL("2015-01-11-minimal.html")
# pandoc(fn, format = "docx") # prodces the .docx file - Word doc.
# rmarkdown::render(fn) # produces table of contents (and html?)
# rmarkdown::render(fn, pdf_document()) # and knit2html() to get .html from .md
title: Minimal
#
# like categories, tags can be specified as a YAML list or a space- separated string.
# http://en.wikipedia.org/wiki/YAML#Lists
type: posts
layout: post
tags:
- Rminimal
- sparklineminimal plotminimal
categories: rstatsminimal sparklineminimal
output:
  # https://github.com/jimhester/knitrBootstrap
  # http://cran.r-project.org/web/packages/knitrBootstrap/README.html
  # ::bootstrap_document custom rendering function for the Rmarkdown package.
  knitrBootstrap::bootstrap_document: #  to create bootstrap styled HTML reports - not .md
    # https://github.com/jimhester/knitrBootstrap#package-options
    # title: "where does this appear? # (NULL) Set the title for the html document
    # http://bootswatch.com/ optionally including a dynamic style switch.
    theme: Cyborg # monokai cyborg slate darkly superhero cerulean 
    theme.chooser: TRUE # (FALSE) - Add a bootstrap style chooser to the page.
    # highlight Set the default code style. (HighlightJS)
    # https://github.com/jimhester/knitrBootstrap#highlight-themes
    highlight: monokai # Sunburst # Zenburn # HighlightJs # google code 
    highlight.chooser: TRUE # (FALSE) - Add a code style chooser to the page.
    menu: TRUE # FALSE # Whether to include the bottom navbar.
author: ttmmghmm
---


```{r Change-default-global-options, eval = TRUE, echo = FALSE, results='hide'}
# See boiler_plate_vignette_setup.Rmd for default global settings.

```


```{r child = c('../_posts/boiler_plate_vignette_setup.Rmd', '../_posts/boiler_plate_bibliography_start.Rmd') }
# child: (NULL; character) a character vector of filenames of child documents to be run and input into the main document http://yihui.name/knitr/options/
# http://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output
```

```{r}
library(fitdistrplus)
library(logspline)
```

The data is masked for brevity.
```{r dataButDontItInFull, echo=FALSE}
str(x <- c(37.50,46.79,48.30,46.04,43.40,39.25,38.49,49.51,40.38,36.98,40.00,
38.49,37.74,47.92,44.53,44.91,44.91,40.00,41.51,47.92,36.98,43.40,
42.26,41.89,38.87,43.02,39.25,40.38,42.64,36.98,44.15,44.91,43.40,
49.81,38.87,40.00,52.45,53.13,47.92,52.45,44.91,29.54,27.13,35.60,
45.34,43.37,54.15,42.77,42.88,44.26,27.14,39.31,24.80,16.62,30.30,
36.39,28.60,28.53,35.84,31.10,34.55,52.65,48.81,43.42,52.49,38.00,
38.65,34.54,37.70,38.11,43.05,29.95,32.48,24.63,35.33,41.34))
```

Now lets use descdist:
```{r}
descdist(x, discrete = FALSE, boot = 5e2)
```

```{r fitTheData}
fit.weibull <- fitdist(x, "weibull")
fit.norm <- fitdist(x, "norm")
```
```{r plotTheData}
plot(fit.norm)
```

```{r theFit}
fit.norm$aic
```


As explained here, we can use bootstrapping to add pointwise confidence intervals to the estimated Weibull PDF or CDF:

```{r cis}
xs <- seq(10, 65, len=500)

n <- 1e4
true.weibull <- rweibull(n, shape= fit.weibull$estimate["shape"]
                             , scale = fit.weibull$estimate["scale"])

nn <- 1e2
boot.pdf <- sapply(1:nn, function(i) {
  xi <- sample(x, size=length(x), replace=TRUE)
  MLE.est <- suppressWarnings(fitdist(xi, distr="weibull"))  
  dweibull(xs, shape=MLE.est$estimate["shape"],  scale = MLE.est$estimate["scale"])
}
)

boot.cdf <- sapply(1:nn, function(i) {
  xi <- sample(x, size=length(x), replace=TRUE)
  MLE.est <- suppressWarnings(fitdist(xi, distr="weibull"))  
  pweibull(xs, shape= MLE.est$estimate["shape"],  scale = MLE.est$estimate["scale"])
}
)   
```

```{r plotTheCis}
#-----------------------------------------------------------------------------
# Plot PDF
#-----------------------------------------------------------------------------

par(bg="white", las=1, cex=1.2)
plot(xs, boot.pdf[, 1], type="l", col=rgb(.6, .6, .6, .1), ylim=range(boot.pdf),
     xlab="x", ylab="Probability density")
for(i in 2:ncol(boot.pdf)) lines(xs, boot.pdf[, i], col=rgb(.6, .6, .6, .1))

# Add pointwise confidence bands

quants <- apply(boot.pdf, 1, quantile, c(0.025, 0.5, 0.975))
min.point <- apply(boot.pdf, 1, min, na.rm=TRUE)
max.point <- apply(boot.pdf, 1, max, na.rm=TRUE)
lines(xs, quants[1, ], col="red", lwd=1.5, lty=2)
lines(xs, quants[3, ], col="red", lwd=1.5, lty=2)
lines(xs, quants[2, ], col="darkred", lwd=2)
```

# sparkline example

```{r API}
x = rnorm(20)
library(sparkline)
sparkline(x)
sparkline(x, type = 'bar')
sparkline(x, type = 'box')
```

#Inline line graphs `r sparkline(x)`

Bar charts  `r sparkline(abs(x), type = 'bar')`  
negative values: `r sparkline(x, type = 'bar')`

# table
```{r}
y <- runif(20)
```

| Stock | Sparkline         | Boxplot  
|-------|-------------------|--------
| x     | `r sparkline(x)`  | `r sparkline(x, type ='box')`
| y     | `r sparkline(y)`  | `r sparkline(y, type ='box')`



```{r child = c('../_posts/boiler_plate_reproducibility.Rmd', '../_posts/boiler_plate_bibliography_end.Rmd') }
```
