---
yamlFileName: 2015-01-10-sparkline.Rmd # WARNING: update the filename?
# print(rmarkdown::metadata$yamlFileName) # permalink
# library(knitr)
# setwd("~/git/ttmmghmm.github.io/_drafts") ; fn <- "2015-01-10-sparkline.Rmd" ; knit(fn)  # to get the .md file 
#
# library(knitrBootstrap)
# rmarkdown::render(fn, knitrBootstrap::bootstrap_document(), clean = FALSE) # no md?
# produce an identical result to Knit HTML in RStudio- no run-time dependency on RStudio
# https://github.com/jimhester/knitrBootstrap#bootstrap-themes
#   knit(fn) ; markdownToHTML("foo.md") ; browseURL("foo.html")
# pandoc(fn, format = "docx") # prodces the .docx file - Word doc.
# rmarkdown::render(fn) # produces table of contents (and html?)
# rmarkdown::render(fn, pdf_document()) # and knit2html() to get .html from .md
title: "sparkline"
#
# like categories, tags can be specified as a YAML list or a space- separated string.
# http://en.wikipedia.org/wiki/YAML#Lists
type: posts
layout: post
tags:
- Rwww
- plotwwww
categories: rstatswww dddd
author: ttmmghmm
---

# Displaying an index of posts
* {{ site.posts }}
* {% for post in site.posts %}
    <li>
      <a href="{{ post.url }}">{{ post.title }}</a>
    </li>
  {% endfor %}
<!-- http://jekyllrb.com/docs/collections/
{{ con tent }}
{{ out put }}
-->
# Change the default global options
https://github.com/jimhester/knitrBootstrap#chunk-options
```{r, eval = TRUE}
library(magrittr)
# https://github.com/jimhester/knitrBootstrap#chunk-options
# colors() [grep(patt = "dark", x = colours())]
#     panel: FALSE #  Use panels rather than buttons to toggle blocks.
opts_chunk$set(fig.width = 5, fig.height = 5)
# bootstrap.panel (FALSE) - panels rather than buttons to toggle blocks.
opts_chunk$set(background = c('gray10'), panel = TRUE) 
# http://getbootstrap.com/css/#grid
# bootstrap.thumbnail - (TRUE) - Thumbnail and lightbox images.
opts_chunk$set(thumbnail = TRUE, thumbnail.size = 'col-md-2')
# .class ('row') - class to apply to the div containing the chunk.
# opts_chunk$set(class = 'rowew')
# bootstrap.show.code - (TRUE) - Code from this chunk starts as shown.
# opts_chunk$set(code = FALSE, output = FALSE) 
# opts_chunk$set(echo = FALSE, cache = FALSE)
# opts_chunk$set(message = FALSE, warning = FALSE, error = FALSE) 

# NOT working?
# The package options can be changed using the object opts_knit; for example,
opts_knit$set(progress = TRUE, verbose = TRUE)
```


```{r child = c('../_posts/boiler_plate_vignette_setup.Rmd', '../_posts/boiler_plate_bibliography_start.Rmd') }
# child: (NULL; character) a character vector of filenames of child documents to be run and input into the main document http://yihui.name/knitr/options/
# http://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output
```


http://www.htmlwidgets.org/develop_intro.html

https://github.com/htmlwidgets/sparkline



```{r installSparkline, eval = FALSE}
library(devtools)
install_github('htmlwidgets/sparkline')
```

http://stats.grok.se retrieves Wikipedia page access statistics on a daily basis. 
The information is either presented in HTML or provided as JSON data.

The API is pretty simple
```{r API}
x = rnorm(20)
library(sparkline)
sparkline(x)
sparkline(x, type = 'bar')
sparkline(x, type = 'box')
```
You can also use it in an R Markdown document.

<pre>
---
title: "jquery Sparkline HTML Widget"
author: "Ramnath Vaidyanathan"
date: "July 18, 2014"
output: html_document
---
</pre>

```{r}
library(htmlwidgets)
library(sparkline)
set.seed(1234)
x = rnorm(10)
y = rnorm(10)
```


Inline line graphs `r sparkline(x)`

Bar charts  `r sparkline(abs(x), type = 'bar')`  negative values: `r sparkline(x, type = 'bar')`

| Stock | Sparkline         | Boxplot  
|-------|-------------------|--------
| x     | `r sparkline(x)`  | `r sparkline(x, type ='box')`
| y     | `r sparkline(y)`  | `r sparkline(y, type ='box')`



```{r child = c('../_posts/boiler_plate_reproducibility.Rmd', '../_posts/boiler_plate_bibliography_end.Rmd') }
```
<!-- 
# boiler_plate_bibliography_end has to come last else references in boiler_plate_reproducibility are lost!
-->

