<!-- *** reproducibility *** 
NB: Do not add yaml code here, put it at the start of the top level Rmd 
-->

# Reproducibility
This final section highlights how this vignette was created.

## To recreate this vignette
This vignette was generated using:    

<!-- 
-->
Additional semantic markup can be added the the citations themselves, such as the reason for the citation. 
https://github.com/trinker/knitcitations 

* `knitrBootstrap` ` knitcitations::citep(bib[['knitrBootstrap']], , cito = "usesMethodIn")`
* Running behind the scenes:  
    * `knitr` ` knitcitations::citep(bib[['knitr']])` 
    * `rmarkdown` ` knitcitations::citep(bib[['rmarkdown']])` 

```{r boiler_plate_reproducibility, eval=FALSE, bootstrap.show.code=FALSE}
# TODO: parse permalink? varialble
print(rmarkdown::metadata$yamlFileName) # permalink
docName <- rmarkdown::metadata$yamlFileName

## Create the vignette
library('knitrBootstrap') 
knitrBootstrapFlag <- packageVersion('knitrBootstrap') < '1.0.0'
if(knitrBootstrapFlag) {
    ## CRAN version
    library('knitrBootstrap')
    cat("\n\n\tmetadata:title", rmarkdown::metadata$title, "\n\n")
    # TODO: stopifnot(file.exists(paste0(rmarkdown::metadata$title, ".Rmd")))
    print(system.time(knit_bootstrap(docName, chooser=c('boot', 'code'), show_code = TRUE)))
    # unlink('dots.md') # why remove .md file and in yaml?
} else {
    ## GitHub version
    library('rmarkdown')
    print(system.time(render(docName)))
}
unlink('citations.bib')
## Note: if you prefer the knitr version use:
# library('rmarkdown')
# system.time(render(docName, 'html_document'))

## Extract the R code
library('knitr')
knit(docName, tangle = TRUE)

KnitPost <- function(input, base.url = "/") {
    require(knitr)
    opts_knit$set(base.url = base.url)
    fig.path <- paste0("figs/", sub(".Rmd$", "", basename(input)), "/")
    opts_chunk$set(fig.path = fig.path)
    opts_chunk$set(fig.cap = "center")
    render_jekyll()
    knit(input, envir = parent.frame())
}
# TODO: insert the file name dynamically (both from _drafts and _posts?)
KnitPost(docName)

```

## YAML boiler plate
```{r YAML setup, echo=TRUE}
str(rmarkdown::metadata) # https://github.com/rstudio/rmarkdown/issues/260
```

## `R` information

### Session and packages
```{r session information, echo=FALSE, bootstrap.show.code=FALSE, bootstrap.show.message=FALSE}
## Session info
library('devtools')
options(width = 90)
session_info()
```

### Runtime 
```{r processing time, echo=FALSE, bootstrap.show.code=FALSE, message=FALSE, warning = FALSE, results='hide'} 
## Processing time in seconds
totalTime <- diff(c(startTime, Sys.time()))
userTime <- round(totalTime, digits = 1)
```
Vignette generated in `r userTime` seconds.   
<p>Timestamp `r Sys.time()`. <!-- Date the vignette was generated -->
