---
title: List of TODOs
# permalink: If you need your processed blog post URLs to be something other than the default /year/month/day/title.html then you can set this variable and it will be used as the final URL.
# tags : [ python, jekyll, R, R-Bloggers, Jekyll, github ]
tags:
- TODO
- R-Bloggers
categories:
- rstats
- reproducibility
# published = false => Jekyll will not process the file. Else Rmd file appears as a blog with html file i.e. 2 posts.
published: true
status: publish
# output: ioslides_presentation
output:
  knitrBootstrap::bootstrap_document:
    # title: "where does this appear?  - bootstrap web page style"
    theme: cyborg # cyborg slate cerulean
    highlight: google code # sunburst
    theme.chooser: TRUE
    highlight.chooser: TRUE
    menu: FALSE
  #html_document:
  #  toc: true
  #  theme: united
  # http://rmarkdown.rstudio.com/html_fragment_format.html
  # html_fragment - no title/author - excl std hdr content. HTML within larger web sites (e.g. blogs).
  #html_fragment: 
  #  toc: true
    # united zenburn
    # theme: united # maybe theme is for html_document: only
  #  number_sections: true
  #  keep_md: false
  # rmarkdown::render(fn) # produces table of contents and united theme
  # render(fn, pdf_document()) # library(rmarkdown) ; # knit2html() 
  pdf_document:
    toc: true
    theme: united # maybe theme is for html_document: only
    highlight: zenburn
author: "ttmmghmm"
layout: post
# http://vitobotta.com/how-to-migrate-from-wordpress-to-jekyll/
# paginate: 3 # it lets you choose how many posts to show per page - overrides _config.yml
# language: R # ~~~ R
# type: post # ??
# fontsize: 18pt # does not work
# classoption: landscape
---


# What they dont tell you about Rmarkdown
## Lists
* Unordered lists should be a doddle but there are gotchas.
* The first element in a list _must_ be preceeded by a blank line before the first item.
    * Ending the preceeding line with two or more spaces does not seem to work.
        * Even though it is documented to.
    * Neither does ending the line with html like < b r >.
        * TODO: how to do a literal quote.
* You need to put two tabs at the start of a sub item.
    + Else the subitem will not render as a subitem in your list.



```{r child = '../_posts/boiler_plate_vignette_setup.Rmd'}
# http://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output
```

```{r child = '../_posts/boiler_plate_bibliography_start.Rmd'}
```

# GuardianR
```{r 'GuardianR'}
library(GuardianR)
results <- get_guardian("islamic+state",
  from.date="2014-09-16",
  to.date="2014-09-16",
  api.key="3xzg2fk53jcdgaj5tbwqqhcz")
```


* http://cran.r-project.org/web/packages/GuardianR/GuardianR.pdf


# Bitcoin
http://beautifuldata.net/2015/01/querying-the-bitcoin-blockchain-with-r/


# APIs
## public
http://opendata.stackexchange.com/questions/1677/a-web-api-users-guide-for-free-and-open-data?newsletter=1&nlcode=386863%7c20e3
  
# Wikipedia
* Tags: text mining
* Packages: tm

## Graph and web crawling
* http://semanticweb.cs.vu.nl/R/wikipedia_graph/wikipedia_graph.html
* Tags: [text mining, graphs, wikipedia, crawl, Simple Wikipedia, Wikipedia,
  analytical metrics]
  * “Basic English 850 basic English words chosen by Charles Kay Ogden.”
* TODO: dynamic graph, shiny

## WikiPediR package
* http://www.rexamine.com/2014/06/text-mining-in-r-automatic-categorization-of-wikipedia-articles/
  *  hierarchical categorization of Wikipedia articles
* more information about text mining in R: 
    * http://onepager.togaware.com/TextMiningO.pdf
    * http://cran.r-project.org/web/views/NaturalLanguageProcessing.html
    * http://www.r-bloggers.com/text-mining/
    * http://www.jstatsoft.org/v25/i05/paper
    * http://www.r-bloggers.com/visualising-wikipedia-search-statistics-with-r/
        * search traffic for any article - search statistics for “Financial crisis”. 
            * The wikiStat() function returns dataframe with the necessary data.
    * http://cran.r-project.org/web/packages/tm.plugin.webmining/vignettes/ShortIntro.pdf

```{r, eval = FALSE}
opts_chunk$set(eval = FALSE)
library(magrittr)
docs[[1]]
# Replace all “” elements with a space. 
# We do it because there are not a part of text document but in general a html code.
# use the non-greedy .*? match - match up until the first following instance of '>'. Without this, if you use just .*, you'll capture everything up to the last '[END DATA]'>'.
docs2 <- tm_map(docs, function(x) stri_replace_all_regex(x, "<.+?>", " "))
docs3 <- tm_map(docs2, function(x) stri_replace_all_fixed(x, "\t", " "))
docs2[[1]]

docs4 <- tm_map(docs3, PlainTextDocument)
docs5 <- tm_map(docs4, stripWhitespace)
docs6 <- tm_map(docs5, removeWords, stopwords("english"))
docs7 <- tm_map(docs6, removePunctuation)
docs8 <- tm_map(docs7, tolower)

docs8[[1]]

docs %>% 
  tm_map(FUN = function(x) stri_replace_all_regex(x, "<.+?>", " ")) ->  
docs2 
```





```{r child = '../_posts/boiler_plate_reproducibility.Rmd'}
```

```{r child = '../_posts/boiler_plate_bibliography_end.Rmd'}
# boiler_plate_bibliography_end has to come last else references in boiler_plate_reproducibility are lost!
```

