---
title: "h20"
author: "ttmmghmm"
date: "1/3/2015"
output: html_document
---

http://blog.revolutionanalytics.com/2014/04/a-dive-into-h2o.html


```{r setup h20 if needed, eval=FASLSE}

# The following two commands remove any previously installed H2O packages for R.
if ("package:h2o" %in% search()) { detach("package:h2o", unload=TRUE) }
if ("h2o" %in% rownames(installed.packages())) { remove.packages("h2o") }
 
# Next, we download, install and initialize the H2O package for R.
install.packages("h2o", 
                 repos=(c("http://s3.amazonaws.com/h2o-release/h2o/rel-kahan/5/R", 
                          getOption("repos"))))

```

```{r}
library(h2o)                # Load H2O library  
localH2O = h2o.init()       # initial H2O locl instance 
```

# Run a demo to see H2O at work
```{r Run a demo to see H2O at work}
demo(h2o.glm)
```

# Upload iris file from the H2O package into the H2O local instance
```{r Upload iris file from the H2O package into the H2O local instance}
iris.hex <-  h2o.uploadFile(localH2O, 
                            path = system.file("extdata", "iris.csv", package="h2o"), 
                            key = "iris.hex")
summary(iris.hex)
```

# R v h20 output
However, the apply() function from the H2O R package behaves a bit differently
```{r R v h20 output}
x <- apply(iris.hex[,1:4],2,sum)
x
```
Instead of returning the results, it returns the attributes of file in which the results are stored. You can see this from looking at the structure of x.
```{r}
str(x)
#You can get the data out, by coercing x into being a data frame.
df <- as.data.frame(x)
df
```

# H2O R package functions 
'ddply()' features for H2O data sets. 

* h2o.ddply()
* h2o.addFunction()

# Push a new function into the H2O JVM

# Large _local_ dataset 
The following code loads one year of the airlines data set from my hard drive into the H2O instance, gives me the dimensions of the data, and lets me know what variables I have.
```{r, eval = FALSE}
path <- "C:/DATA/Airlines_87_08/2008.csv"
air2008.hex <- h2o.uploadFile(localH2O, path = path,key="air2008")
dim(air2008.hex)
# [1] 7009728 29
colnames(air2008.hex)
```


```{r tidy up}
if ("package:h2o" %in% search()) { detach("package:h2o", unload=TRUE) }
```

