---
title: bootstrap web page style
# permalink: If you need your processed blog post URLs to be something other than the default /year/month/day/title.html then you can set this variable and it will be used as the final URL.
# tags : [ python, jekyll, R, R-Bloggers, Jekyll, github ]
tags:
- jekyll
- R-Bloggers
- R
- plot
- dots
- sessionInfo
categories:
- rstats
- reproducibility
# published = false => Jekyll will not process the file. Else Rmd file appears as a blog with html file i.e. 2 posts.
published: true
status: publish
# output: ioslides_presentation
output:
  knitrBootstrap::bootstrap_document:
    # title: "where does this appear?  - bootstrap web page style"
    theme: cyborg # cyborg slate cerulean
    highlight: google code # sunburst
    theme.chooser: TRUE
    highlight.chooser: TRUE
    menu: FALSE
  #html_document:
  #  toc: true
  #  theme: united
  # http://rmarkdown.rstudio.com/html_fragment_format.html
  # html_fragment - no title/author - excl std hdr content. HTML within larger web sites (e.g. blogs).
  #html_fragment: 
  #  toc: true
    # united zenburn
    # theme: united # maybe theme is for html_document: only
  #  number_sections: true
  #  keep_md: false
  # rmarkdown::render(fn) # produces table of contents and united theme
  # render(fn, pdf_document()) # library(rmarkdown) ; # knit2html() 
  pdf_document:
    toc: true
    theme: united # maybe theme is for html_document: only
    highlight: zenburn
author: "ttmmghmm"
layout: post
# http://vitobotta.com/how-to-migrate-from-wordpress-to-jekyll/
# paginate: 3 # it lets you choose how many posts to show per page - overrides _config.yml
# language: R # ~~~ R
# type: post # ??
# fontsize: 18pt # does not work
# classoption: landscape
---



```{r child = '../_posts/boiler_plate_vignette_setup.Rmd'}
# http://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output
```

```{r child = '../_posts/boiler_plate_bibliography_start.Rmd'}
```

```{r, eval = FALSE, results = 'hide', echo = FALSE}
# fn <- "2014-12-28-test-post-3.Rmd"
# library(knitr) ; knit(fn)  # produces the md file
# pandoc(fn, format = "docx") # prodces the .docx file
# render("2014-12-28-test-post-3.Rmd", pdf_document()) 
# library(rmarkdown) ; # knit2html() 

```

for __R__'s `par()` function
Here we used the ```png``` library and the ```rasterImage()``` command to read in and 
of your __R__ plot device, and it will not stay consistent if you resize.
{% highlight r %}
plot(1:10)
# Note that the rectangle we make here has corner coordinates outside of
{% endhighlight %}
Now let's say we want to __add a logo__ or other external image in the margin 


# Bibliography

This vignette was generated using `knitrBootstrap` `r citep(bib[['knitrBootstrap']])`
with `knitr` `r citep(bib[['knitr']])` and `rmarkdown` `r citep(bib[['rmarkdown']])` running behind the scenes.

Citations made with `knitcitations` `r citep(bib[['knitcitations']])`.

```{r vignetteBiblio, results='asis', echo=FALSE}
## Print bibliography
bibliography()
```

\newpage
\pagebreak


```{r child = '../_posts/boiler_plate_reproducibility.Rmd'}
```

```{r child = '../_posts/boiler_plate_bibliography_end.Rmd'}
# boiler_plate_bibliography_end has to come last else references in boiler_plate_reproducibility are lost!
```

